Bird beak's elaboration and innovation

### 2022-06-14 Analysis/10-sensitivity_analysis.Rmd
Update 10-sensitivity_analysis.Rmd

      ## Simulate the space
      return(sapply(space_var_prop, function(var, tree) phytools::fastBM(tree = tree, sig2 = var), tree))
}

@@

## Setting up 20 random replicates
for(i in 1:25) {
      ## Set up the mini-chains models
      randospace_charadriiformes_ <- make.mini.chains(
                                      data         = BMise.space(shapespace, tree, selected_dim),
                                      dimensions   = selected_dim,
                                      tree         = trees_list[sample(1:1000, 400)],
                                      trait.family = "gaussian",
                                      randoms      = c("global", "level1"),
                                      residuals    = "global",
                                      priors       = est_params$priors,
                                      verbose      = TRUE,
                                      parameters   = list(
                                            nitt   = est_params$burnin + thin * samples,
                                            thin   = thin,
                                            burnin = est_params$burnin))
      ## Save the mini.chains
      save(randospace_charadriiformes_, file = paste0("../Data/Cluster/shapespace_charadriiformes/randospace_charadriiformes_", i, ".mini.chains"))
}
```

@@

Model | parameters | replicates | trees sampled | spaces sampled | posterior VCVs |
------|------------|------------|---------------|----------------|----------------|
shapespace | from shapespace | 100 | 1 | 1000
randomspace | from shapespace | 100 | 25 | 1000
BMspace | from shapespace | 100 | 25 | 1000
ballspace | from ballspace | 100 | 1 | 1000

>>>>

      ## Simulate the space
      BMspace <- as.data.frame(sapply(space_var_prop, function(var, tree) phytools::fastBM(tree = tree, sig2 = var), tree))

      ## Match the species with the correct levels
      BMspace <- BMspace[match(space$animal, rownames(BMspace)), ]
      BMspace$level1 <- space$level1
      BMspace$animal <- space$animal
      return(BMspace)
}

@@

```{r, eval = FALSE, echo = FALSE}
## Loading the parametrisation data
load(file = "../Data/Processed/shapespace_charadriiformes_family.rda")

## Select the data
shapespace <- shapespace_charadriiformes_family[[1]]$space
selected_dim <- shapespace_charadriiformes_family[[1]]$dimensions
consensus_tree <- shapespace_charadriiformes_family[[1]]$consensus_tree
trees_list <- shapespace_charadriiformes_family[[1]]$trees_list

for(i in 1:25) {
      ## Create the space
      BM_space <- BMise.space(shapespace, tree, selected_dim)

      ## Set up the parametrising chains models
      param_chains <- make.mini.chains(data         = BM_space,
                                       dimensions   = selected_dim,
                                       tree         = consensus_tree,
                                       trait.family = "gaussian",
                                       randoms      = c("global", "level1"),
                                       residuals    = "global",
                                       priors       = 0.02,
                                       verbose      = TRUE,
                                       parameters   = list(
                                             nitt   = 20000,
                                             thin   = 500,
                                             burnin = 0))

      ## Run the parametrisation chains (local)
      params <- run.mini.chains(param_chains, replicates = 3)

      ## Get the estimated parameters
      est_params <- extract.parameters(params)

      ## The thinning parameter
      thin <- 200
      ## The number of samples per chains
      samples <- 10

      ## Setting up 20 random replicates
      ## Set up the mini-chains models
      BMspace_charadriiformes_ <- make.mini.chains(
                                      data         = BM_space,
                                      dimensions   = selected_dim,
                                      tree         = trees_list[sample(1:1000, 400)],
                                      trait.family = "gaussian",
                                      randoms      = c("global", "level1"),
                                      residuals    = "global",
                                      priors       = est_params$priors,
                                      verbose      = TRUE,
                                      parameters   = list(
                                            nitt   = est_params$burnin + thin * samples,
                                            thin   = thin,
                                            burnin = est_params$burnin))
      ## Save the mini.chains
      save(BMspace_charadriiformes_, file = paste0("../Data/Cluster/shapespace_charadriiformes/BMspace_charadriiformes_", i, ".mini.chains"))
}
```

@@

Model       | parameters      | replicates | trees sampled | spaces sampled | posterior VCVs |
------------|-----------------|------------|---------------|----------------|----------------|
shapespace  | from shapespace | 100        | 100           | 1              | 1000 |
randomspace | from shapespace | 100        | 100           | 25             | 1000 |
BMspace     | from shapespace | 100        | 100           | 25             | 1000 |
ballspace   | from ballspace  | 100        | 100           | 1              | 1000 |

# Analysing the results
